---
title: "Untitled"
author: "Aimee Gott"
date: "20 September 2015"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Including a Shiny Component

The following is an example of how we can include a shiny component inside a markdown document.

```{r, echo=FALSE}
inputPanel(
  numericInput(inputId = "num", label = "Number of Simulations:", value = 100),
  
  textInput(inputId = "title", label = "Enter title text:")
)

data <- reactive(rnorm(input$num))
  
renderPlot({
    
    hist(data(), main = input$title, xlab = "Simulated Data")
    
    })

```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package = "shiny"),
  options = list(
    width = "100%", height = 550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



